NumPy---Array Programming in Python

### 2020-01-25 body.tex
Minor edits

@@

The \emph{practical} appeal of NumPy and its ecosystem is apparent
when you consider the following description of how APL users
work---one which
easily applies to scientific Python users too \cite{kromberg2007apl}:
\begin{quote}
Users of APL tend to ``live in their data''. Interactive interpreters allow them
to inspect, almost feel their  way forward, discovering successful snippets
of code through experimentation and collecting them
into imperative or functional programs according to taste.
\end{quote}

This modality of interactive scientific exploration would develop
further and eventually culminate in the Jupyter ecosystem of tools \fixme{citation needed}.

NumPy also benefited from being written in Python, a
general-purpose language well-suited to standard programming tasks such as
cleaning data, interacting with web resources, and parsing text.
Adding fast array operations and linear algebra allows scientist to do all
their work with within a single language---and one that has the advantage of
being famously easy to learn and teach.  In fact, Python's adoption as
a primary learning language in many universities \fixme{citation
needed} may well have further popularize NumPy as a tool of choice for
modern data science.

>>>>

This includes popular tensor computation libraries such as
CuPy\footnote{\url{https://cupy.chainer.org/}},
JAX\footnote{\url{https://jax.readthedocs.io/en/latest/jax.numpy.html}}, and
Apache MXNet\footnote{\url{https://numpy.mxnet.io/}}.
PyTorch\footnote{\url{https://pytorch.org/tutorials/beginner/blitz/tensor\_tutorial.html}}
and
Tensorflow\footnote{\url{https://www.tensorflow.org/tutorials/customization/basics}}
provide tensor APIs with NumPy-inspired semantics.

@@

The \emph{practical} appeal of NumPy and its ecosystem is apparent
when you consider the following description of how APL users
work---one which
easily applies to scientific Python users too \cite{kromberg2007apl}:
\begin{quote}
Users of APL tend to ``live in their data''. Interactive interpreters allow them
to inspect, almost feel their  way forward, discovering successful snippets
of code through experimentation and collecting them
into imperative or functional programs according to taste.
\end{quote}
This modality of interactive scientific exploration would develop
further and eventually culminate in the Jupyter ecosystem of tools \cite{Kluyver:2016aa}.

NumPy also benefited from being written in Python, a
general-purpose language well-suited to standard programming tasks such as
cleaning data, interacting with web resources, and parsing text.
Adding fast array operations and linear algebra allows scientist to do all
their work with within a single language---and one that has the advantage of
being famously easy to learn and teach.  In fact, Python's adoption as
a primary learning language in many universities (e.g., at UC Berkeley
many lower division courses use Python including Foundations of Data Science,
Introduction to Computational Thinking with Data,
and The Structure and Interpretation of Computer Programs) have
further popularized NumPy as a tool of choice for modern data science.
